---
title: "Google Sheets JSON"
author: "Eric He"
date: "August 21, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("googlesheets") # manipulate google sheets
library("dplyr") # munge data
library("jsonlite") # write to JSON
library("purrr") # functionals
library("stringr") # text processing
```

Give R permission to control your Google Sheet. This only needs to be done once per account.

```{r}
gs_auth()
```

Extract the key we can use to control the Google Sheet from within R.

```{r}
key <- extract_key_from_url("https://docs.google.com/spreadsheets/d/1xvODUunKQ1RUQykaoE778REOz4iRSoVQtBfMt5fVqkw/edit#gid=0")
```

Register the key with R.

```{r}
bap <- gs_key(key)
```

Let's take a look.

```{r}
bap
```

The worksheet names alone can be extracted with this command.

```{r}
names <- gs_ws_ls(bap)
names
```

We can edit the google sheets from within R now, but for this exercise I'll just download the csv files.

```{r}
(sheeeeet <- map(names, gs_read_csv, ss = bap))
```

This is a list of data frames which we can easily manipulate.

Let's build the JSON. I've set the pretty argument to TRUE for viewing purposes.

```{r}
map(sheeeeet, toJSON, pretty = TRUE) %>%
  reduce(cat) # I use cat to print the output here, but paste is the function to store the output
```

The paste function used to reduce the list of JSON files into one is incorrect. I've looked for a function to combine these correctly but it seems the JSONlite package does not have it. I'll probably just write a custom function to preprocess the data so that it can be pasted correctly.

Let's recap the entire script.

```{r}
library("googlesheets")
library("dplyr")
library("jsonlite")
library("purrr")

sheets_url <- "https://docs.google.com/spreadsheets/d/1xvODUunKQ1RUQykaoE778REOz4iRSoVQtBfMt5fVqkw/edit#gid=0"
json_file <- "sandbox2.json"

key <- extract_key_from_url(sheets_url)
bap <- gs_key(key)
names <- gs_ws_ls(bap)
sheeeeet <- map(names, gs_read_csv, ss = bap)
jsoooon <- map(sheeeeet, toJSON, pretty = TRUE) %>%
  map2(names, fix_json) %>%
  reduce(paste, sep = "\n")

write(jsoooon, file = json_file)
```
Code rewritten from a functional programming perspective. The codeblock can be wrapped inside a single function.

Theoretically flexible for any number of sheets, sheet names, tidy data structures. However, Google Drive limits the amount of requests that can come in to around 6 sheets at a time, so be careful. 

```{r}
sheets_url <- "https://docs.google.com/spreadsheets/d/1xvODUunKQ1RUQykaoE778REOz4iRSoVQtBfMt5fVqkw/edit#gid=0"

sheets_url %>%
  extract_key_from_url %>%
  gs_key %>%
  gs_ws_ls %>%
  map(gs_read_csv, ss = bap) %>%
  map(toJSON, pretty = TRUE) %>%
  reduce(paste) %>%
  write("sandbox.json")

#file_name input must be character

gs_to_json <- function(url, file_name){
  url %>%
  extract_key_from_url %>%
  gs_key %>%
  gs_ws_ls %>%
  map(gs_read_csv, ss = bap) %>%
  map(toJSON, pretty = TRUE) %>%
  reduce(paste, sep = "\n") %>%
  write(file = file_name)
}
```

Write a function to fix the JSON output.

Replace [ with {, ] with }.
Put name of sheet in the beginning.

```{r}
c <- str_replace(b, pattern = '\\[', replacement = "\\[\"master\":")
d <- str_replace(c, pattern = "\\[", replacement = "\\{")
e <- str_replace(d, pattern = "\\]", replacement = "\\}")

fix_json <- function(json_obj, json_name){
  formatted_name <- paste0("\\[\"", json_name, "\":")
  str_replace(json_obj, pattern = "\\[", replacement = formatted_name) %>%
  str_replace(pattern = "\\[", replacement = "\\{") %>%
  str_replace(pattern = "\\]", replacement = "\\}") %>%
    return()
}
```
