---
title: "Suggesting-Big-Little-Pairings"
author: "Eric He"
date: "September 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("purrr")
library("googlesheets") # manipulate google sheets
library("dplyr") # munge data
library("jsonlite") # write to JSON
library("purrr") # functionals
library("stringr") # text processing
library("googledrive")
```

```{r}
gs_auth()
```

```{r}
sheets_table <- gs_ls()
```

Generate synthetic data. We have 33 candidates and 10 mentors. For each candidate, we select 5 random mentors and vice versa. Profession and hobby interests are also randomly generated.

```{r}
candidates_key <- filter(sheets_table, sheet_title == "BAP Fall 2017 Ranking Application (for Mentees) (Responses)") %>% 
  pull(sheet_key)
candidates_raw <- candidates_key[1] %>%
  gs_key %>%
  gs_read_csv()

mentors_key <- filter(sheets_table, sheet_title == "BAP Fall 2017 Ranking Application (for Mentors) (Responses)") %>% 
  pull(sheet_key)
mentors_raw <- mentors_key %>%
  gs_key %>%
  gs_read_csv()
```

```{r}
candidates_raw
```

```{r}
mentors_raw
```

Write the function to calculate hobby and profession similarity scores.

```{r}
score_calculator <- function(candidate_info, mentor_info, keyword){
  candidate_mentor_pairing <- map(list(candidate_info, mentor_info), ~select(., starts_with(keyword))) %>%
    map(t) %>%
    map(as.vector) %>%
    map(~subset(., !is.na(.)))
  candidate_match <- candidate_mentor_pairing[[1]] %in% candidate_mentor_pairing[[2]] %>%
    sum(.) / length(candidate_mentor_pairing[[1]])
  mentor_match <- candidate_mentor_pairing[[2]] %in% candidate_mentor_pairing[[1]] %>%
    sum(.) / length(candidate_mentor_pairing[[2]])
  score <- mean(c(candidate_match, mentor_match))
  return(score)
}
```

For one candidate and one mentor, calculate all the relevant info.

```{r}
candidate_name <- "Bill He"
mentor_name <- "Bill Shen"

one_candidate_one_mentor <- function(candidate_name, mentor_name){
candidate_info <- filter(candidates_raw, Name == candidate_name)
mentor_info <- filter(mentors_raw, Name == mentor_name)

valid_match <- candidate_info$Year == "Junior" & mentor_info$Year == "Junior"

profession_score <- score_calculator(candidate_info, mentor_info, keyword = "Profession")
hobby_score <- score_calculator(candidate_info, mentor_info, keyword = "Hobbies")

candidate_ranking_of_mentor <- which(as.character(mentor_name) == select(candidate_info, starts_with("Mentor")))[1]
  
mentor_ranking_of_candidate <- which(as.character(candidate_name) == select(mentor_info, starts_with("Mentee")))[1]

row <- data_frame(mentor_name, candidate_name, mentor_ranking_of_candidate, candidate_ranking_of_mentor, profession_score, hobby_score, valid_match)
print(paste("Completed calculation for candidate", candidate_name, "and mentor", mentor_name))
return(row)}
```

Generate scores for all possible candidate-mentor pairings.

```{r}
all_pairings <- expand.grid(candidates_raw$Name, mentors_raw$Name)
finished <- map2_df(all_pairings$Var1, all_pairings$Var2, one_candidate_one_mentor) %>%
  filter(valid_match == TRUE) %>%
  arrange(mentor_ranking_of_candidate, candidate_ranking_of_mentor, profession_score, hobby_score)
```

Upload the output to the Google Sheets in the Mentor folder.

```{r}
write.csv(finished, row.names = FALSE, file = "bap_2017_ranking_application_transformed.csv")
sheets_table %>%
  filter(sheet_title == "bap_2017_ranking_application_transformed") %>%
  pull(sheet_key) %>%
  as_id %>%
  drive_update(media = "bap_2017_ranking_application_transformed.csv")
```